---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE, comment = "#>")
library(ifl)
```
# ifl

[![Build status](https://travis-ci.org/mkearney/ifl.svg?branch=master)](https://travis-ci.org/mkearney/ifl)
[![CRAN status](https://www.r-pkg.org/badges/version/ifl)](https://cran.r-project.org/package=ifl)
[![Coverage Status](https://codecov.io/gh/mkearney/ifl/branch/master/graph/badge.svg)](https://codecov.io/gh/mkearney/ifl?branch=master)

<!--#![Downloads](https://cranlogs.r-pkg.org/badges/ifl)
#![Downloads](https://cranlogs.r-pkg.org/badges/grand-total/ifl)-->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

Iterating for loops. A dependency-free purrr-like iterator.

## Installation

Install the development version from Github with:

``` r
## install remotes pkg if not already
if (!requireNamespace("remotes")) {
  install.packages("remotes")
}

## install from github
remotes::install_github("mkearney/ifl")
```


## Mapping functions

### `vap_dbl()`

Iterate over input and return double.

```{r}
## double
vap_dbl(rnorm(5), round, 3)
```

### `vap_chr()`

Iterate over input and return character.

Also, useful shortcut: use formulas with `.x`, just like with the
[**{purrr}**](https://purrr.tidyverse.org) package

```{r}
## character
vap_chr(letters[1:5], ~ paste0(.x, "."))
```

### `vap_lgl()`

Iterate over input and return logical.


```{r}
## logical
vap_lgl(letters[1:5], ~ .x %in% c("a", "e", "i", "o", "u"))
```


### `lap()`

Iterate over input and return list(s).

```{r}
## list of strings
lap(letters[1:5], ~ paste0(.x, "."))

## list of columns
lap(mtcars[1:5, 1:5], as.integer)
```
